---
title: "MSDS 597 HW8"
author: "Shiqin Cai"
date: "November 13, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
source("Cai-functions.R")
```


####1. We clean the WHO data by calling the functions `fix_who_column` and output a 3-column data frame that pulls out the martility rate, lower bound and upper bound as shown below.

```{r}
maternal_mortality_raw <- read_csv("data/xmart.csv")
maternal_mortality <- maternal_mortality_raw
colnames(maternal_mortality)[3:4] <- c("mortality.rate", "attended.births")
mortality_cleaned <- fix_who_column(maternal_mortality$mortality.rate)
head(mortality_cleaned)
```


####2. The `water` dataset below shows the burden of disease due to inadequate hygiene in low- and middle-income countries in 2012. We clean the column `2012` which includes the total number of deaths caused by inadequate water in low- and middle-income countries in 2012. We clean this column and output a 3-column data frame by calling the function `fix_who_column`. The result is shown below.

```{r}
water <- read_csv("data/water_sanitation.csv", skip = 2)
water_cleaned <- fix_who_column(water$`2012`)
head(water_cleaned)
```


