---
title: "MSDS 597 Class 8 Joint Project"
author: "Steve Buyske et al."
date: "11/9/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


```{r functions, echo = FALSE}
clean_who_number_spaces <- function(x, sep = ""){
  ## Change formating of numbers from xxx xxx to xxx,xxx
  library(stringr)
  library(dplyr)
  clean_triplet_pair <- 
    function(x) str_replace(x, "([0-9]{1,3}) ([0-9]{3})", paste0("\\1", sep, "\\2"))
  number_of_iterations <- max(map_int(x, ~ str_count(., " ")), na.rm = TRUE)
  for (i in 1:number_of_iterations){
    x <- clean_triplet_pair(x)
  }
  x
}

```
---

As a starting point, we have just the cleaned maternal mortality dataframe. (Feel free to use my cleaning code as the basis for your own functions.)

```{r maternal_mortality, echo = FALSE, message = FALSE}

maternal_mortality_raw <- read_csv("data/xmart.csv")

maternal_mortality <- maternal_mortality_raw

colnames(maternal_mortality)[3:4] <- c("mortality.rate", "attended.births")
maternal_mortality$mortality.rate <- clean_who_number_spaces(maternal_mortality$mortality.rate)

maternal_mortality <- separate(maternal_mortality, mortality.rate, into = c("mortality.rate", "lower.upper"), sep = "\\[", fill = "right")
maternal_mortality$lower.upper <- str_replace_all(maternal_mortality$lower.upper, "\\]", "")
maternal_mortality <- separate(maternal_mortality, lower.upper, into = c("lower.bound", "upper.bound"), sep = "\\-", fill = "right")

maternal_mortality$mortality.rate <- as.integer(maternal_mortality$mortality.rate)
maternal_mortality$lower.bound <- as.integer(maternal_mortality$lower.bound)
maternal_mortality$upper.bound <- as.integer(maternal_mortality$upper.bound)

maternal_mortality$Year <- as.integer(str_sub(maternal_mortality$Year, 1, 4))
head(maternal_mortality)
```


#**Mara Wood**
For my dataset, I chose to look at the homicide rates. I used my function to clean the columns by removing unnnecessary spaces, and splitting the columns into lower and upper bounds for both the number of homicides and the homicide rate.
```{r MaraWoodWeek8}
library(stringr)
viol_hom <- read_csv("data/VIOLENCE_HOMICIDERATE.csv")
colnames(viol_hom)[1:3] <- c("Country", "Num_hom", "Hom_rate")
viol_hom <- viol_hom[-1, ]

source("Wood_functions.R")

fix_who_column(viol_hom$Num_hom)
fix_who_column(viol_hom$Hom_rate)

```