---
title: "Xu_Week_08"
author: "Yankun Xu"
date: "November 11th, 2016"
output: html_document
---

1. Write a set of functions to clean a column in the WHO data from last week. For example, use a modification (no need for commas in the output) of the clean_who_number_spaces() function from class, other functions to pull out the upper and lower bounds, and a function  that calls all of those functions in order to take as input a column in the WHO format and output a 3 column data frame. Name that last function "fix_who_column". Save the functions in a file named along the lines of "buyske-functions.R" (except use your last name, not mine) and save it in the code folder in your copy of the repo described below.

```{r}
source("Xu_Functions.R")

data1<-read.csv("xmart.csv")
colnames(data1)[3]<-"Maternal.Mortality"
colnames(data1)[4]<-"Sklled.Health"

data1_tidy <- fix_who_column(data1$Maternal.Mortality)
glimpse(data1_tidy)
```




2 Here are the details of the problem I described in class
a. Clone the repo at https://github.com/buyske/msds597-week08.git (if there's only a README file and nothing else, though, wait before you clone it). 
b. Pick a data category from http://apps.who.int/gho/data/node.main. Let others in the class know via an Issue to the repo. 
c. Save the file to the data directory in your copy of the rep
d. Add some code to the report.Rmd file to creates a data frame from the data that you chose. Be sure to clean it using your fix_who_column() function.
e. Send a pull request to the original repo.

```{r}
source("Xu_Functions.R")

data2 <- read_csv("DEATHSTOTAL,DEATHS04Y,DALYSTOTAL,DALYS04Y000,DEATHSPER100000,DALYSPER100000.csv")
data2<-filter(data2, X1!="NA")
colnames(data2)[2]<-"Inadequate.water"
data2_tidy <- fix_who_column(data2$Inadequate.water)
glimpse(data2_tidy)
```
